\documentclass[a4paper,10pt]{article}
% \usepackage[utf8]{inputenc}
\usepackage[margin=0.6in]{geometry}
% \usepackage{enumitem}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{fancyhdr}

% Define colors
\definecolor{highlightcolor}{RGB}{0,40,90}


\newcommand{\link}[1]{{\textit{#1}}}

\pagestyle{fancy} % Use fancy header style
\fancyhf{}        % Clear all header and footer fields

% Define the header
\fancyhead[L]{Chandramouli Gnanasambanmdham, Dr.-Ing.}
\fancyhead[C]{}
\fancyhead[R]{\href{mailto:chandramouli681990@gmail.com}{\link{chandramouli681990@gmail.com}}}

% Suppress header and footer on the first page
\fancypagestyle{plain}{
    \fancyhf{} % Clear header and footer for plain style (first page)
    \renewcommand{\headrulewidth}{0pt}
}

\begin{document}

\thispagestyle{plain}

% Header
\begin{center}
    % \textcolor{highlightcolor}{\LARGE \textbf{Chandramouli Gnanasambandham, Dr.-Ing.}}
    {\Large \textbf{Chandramouli Gnanasambandham, Dr.-Ing.}}\\ 
    
    \vspace{0.2cm}
    \small B\"oblingen, Germany \hfill  \bullet  \hfill  +49 \ 179 \ 6588043 \hfill \bullet  \hfill
    \textup{\href{mailto:chandramouli681990@gmail.com}{\link{chandramouli681990@gmail.com}}} \hfill \bullet \hfill
    \textup{\href{https://linkedin.com/in/ganasambandhamc}{\link{Linkedin}}} \hfill \bullet \hfill
    \textup{\href{https://github.com/chandramouli6890}{\link{GitHub}}} \hfill \bullet \hfill
    \textup{\href{https://de.mathworks.com/matlabcentral/profile/authors/4267772}{\link{Matlab}}}

    \vspace{-0.2cm}
    {\rule{\linewidth}{0.8pt}}

    \vspace{0.2cm}
    {\Large \textbf{Software Integration Engineer}}
    
    \vspace{0.1cm}
    \colorbox{gray!40}{%
        \parbox{0.99\textwidth}{%
        \centering \textcolor{highlightcolor}{\textbf{Advancing Intelligent Vehicles with Expertise in System Integration and Scalable Software Architectures}}
        }%
    }
\end{center}


\noindent \textcolor{highlightcolor}{\textit{\textbf{Experienced Automotive
Software Engineer}}} with 12+ years of experience in simulation tool
development, dynamic modeling and C++ programming. Specialized in scalable
software architectures, software quality asurance and physics based simulation.
Strong background in safety critical systems and software validation, with a
proven track record of leading international teams and collaborating with automotive OEMs.

\vspace{0.1cm}
\begin{itemize}
    \item[$\textcolor{highlightcolor}{\checkmark}$] \textcolor{highlightcolor}{\textbf{Led development of physics based vehicle models}} (300+ users) using test-driven development and C++.
    \item[$\textcolor{highlightcolor}{\checkmark}$] \textcolor{highlightcolor}{\textbf{Integrated real-time models into ROS2 simulator}} for V\&V activities, ensuring ISO-26262 compliance.
    \item[$\textcolor{highlightcolor}{\checkmark}$] \textcolor{highlightcolor}{\textbf{Proficient in Git, DevOps and Containerization tools}} for scalable and maintainable software solutions.
    \item[$\textcolor{highlightcolor}{\checkmark}$] \textcolor{highlightcolor}{\textbf{Led collaborative design and development}} of a cutting-edge integration-test-platform for models in Python.
    \item[$\textcolor{highlightcolor}{\checkmark}$] \textcolor{highlightcolor}{\textbf{Played a vital role in providing simulation expertise}} to tune control algorithms for safety-critical systems.
\end{itemize}

\noindent{\rule{\linewidth}{1.4pt}}
\textbf{TECHNOLOGIES \& TOOLS}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

\vspace{-0.4cm}
\noindent
\begin{center}
    \begin{tabular}{ @{\hskip 0pt}m{0.5\textwidth} m{0.5\textwidth} }
        \textcolor{highlightcolor}{\textbf{Languages:}} C/C++, Python, BASH, MATLAB, Julia & \textcolor{highlightcolor}{\textbf{Testing frameworks:}} pytest, Google test \\ 
        \textcolor{highlightcolor}{\textbf{Operating systems:}} Linux (Debian/Ubuntu), Windows & \textcolor{highlightcolor}{\textbf{Debuggers/Profilers:}} \verb|gdb|, \verb|calgrind|, Intel VTune \\
        \textcolor{highlightcolor}{\textbf{Simulation:}} Applied ObjectSim, Simulink, CarMaker & \textcolor{highlightcolor}{\textbf{Middleware \& Comm.:}} ROS2, TCP/IP \\
        \textcolor{highlightcolor}{\textbf{Linear algebra libraries:}} PETSc, EIGEN & \textcolor{highlightcolor}{\textbf{Build Systems}} CMake, Bazel\\
        \textcolor{highlightcolor}{\textbf{DevOps Tools:}} Git, Docker, Jenkins, GitHub actions & \textcolor{highlightcolor}{\textbf{Standards:}} ISO-26262 \\
    \end{tabular}
\end{center}

\vspace{0.1cm}
\noindent{\rule{\linewidth}{1.4pt}}
\textbf{PROFESSIONAL EXPERIENCE}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

\noindent
% \begin{tabular}{ @{\hskip 0pt}m{0.8\textwidth} @{\hskip 0pt}r{0.2\textwidth}}
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{Torc Europe GmbH, Stuttgart, Germany} & \textbf{04/2023 - present}
\end{tabular}

\noindent
\colorbox{gray!40}{%
    \parbox{0.99\textwidth}{%
        \textcolor{highlightcolor}{\textbf{Staff Software Engineer}}
    }%
}

\vspace{0.2cm}
\noindent
\textit{Led development of highly-scalable software tools in C++ using TDD and CI/CD methodologies. }\\

\vspace{-0.3cm}
\noindent
\textbf{Reported to:} Director, Simulation \, \textbf{Direct reports:} 1 Staff, 2 Senior Engineers and 2 Interns \, 
\begin{itemize}[itemsep=0pt, topsep=5pt]
  \item Led interactions with cross-functional teams to identify target use
      cases and requirements for the vehicle models.
  \item Collaborated with OEMs and automotive experts to
      develop scalable validation strategies as per ISO-26262.
  \item Integrated real-time capable vehicle models in a large software project
      using Bazel for validation of AD stack.
  \item Championed software best practices, including code formatting, linting, and peer reviews.
\end{itemize}

\vspace{0.3cm}
\noindent
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{Daimler Truck AG, Stuttgart, Germany} & \textbf{08/2021 - 03/2023}
\end{tabular}

\noindent
\colorbox{gray!40}{%
    \parbox{0.99\textwidth}{%
        \textcolor{highlightcolor}{\textbf{Vehicle Model Engineer}}
    }%
}

\vspace{0.2cm}
\noindent
\textit{Developed multi-fidelity vehicle models using MATLAB/Simulink.}\\

\vspace{-0.3cm}
\noindent
\textbf{Reported to:} Product Owner, Simulation \, \textbf{Direct reports:} 1 Senior Engineer and 2 Interns\,
\begin{itemize}[itemsep=0pt, topsep=5pt]
    \item Developed multi-fidelity vehicle models in MATLAB/Simulink, to enable tuning of motion control parameters.
    \item Implemented a co-simulation interface in C++ to integrate
        high-fidelity truck models, including CAN bus simulations, with AD
        stack, showcasing expertise in system integration and networking
\end{itemize}

\vspace{0.3cm}
\noindent
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{University of Stuttgart, Germany} & \textbf{05/2016 - 04/2021}
\end{tabular}

\noindent
\colorbox{gray!40}{%
    \parbox{0.99\textwidth}{%
        \textcolor{highlightcolor}{\textbf{Academic Researcher}}
    }%
}

\vspace{0.2cm}
\noindent
\textit{Academic Researcher in Particle Dynamics, Software Development, and Experimental Mechanics.}\\
\vspace{-0.4cm}
\noindent
\begin{itemize}[itemsep=0pt, topsep=5pt]
    \item Development and administration of the particle simulation
        software Pasimodo in C++.
    \item Conducted experiments and simulations to determine the optimal
        particle shape for enhanced dissipation, using CAD/3D printing
        technology for validation.
    \item Planning and execution of measurement campaigns of
        virbational structures using Laser-Doppler Vibrometry.
\end{itemize}

\vspace{0.3cm}
\noindent
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{Fraunhofer Institute (ITWM), Kaiserslautern, Germany} & \textbf{10/2015 - 04/2016}
\end{tabular}

\noindent
\colorbox{gray!40}{%
    \parbox{0.99\textwidth}{%
        \textcolor{highlightcolor}{\textbf{Intern}}
    }%
}

\vspace{0.2cm}
\noindent
\textit{Implemented innovative simulation tools to automate vehicle drive data analysis.}

\newpage

\noindent{\rule{\linewidth}{1.4pt}}
\noindent \textbf{EDUCATION}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

\noindent \textbf{Ph.D.\,in Mechanical Engineering}, University of Stuttgart, 2021\\
\noindent \textcolor{highlightcolor}{\textbf{\textit{Grade}}}: Magna Cum Laude $\vert$ \textcolor{highlightcolor}{\textbf{\textit{Thesis}}}: {Particle Dampers - Enhancing Energy Dissipation using Fluid/Solid Interactions and Rigid Obstacle-Grids.}\\

\noindent \textbf{M.Sc.\,in Commercial Vehicle Technology}, Technical University of Kaiserslautern, 2016\\
\noindent \textcolor{highlightcolor}{\textbf{\textit{Grade}}}: 1.9 $\vert$ \textcolor{highlightcolor}{\textbf{\textit{Focus}}}:  Automotive Software Engineering, Embeded Systems, Vehicle Dynamics and Control Theory.\\

\noindent \textbf{B.Eng.\,in Production Engineering}, Anna University, Chennai, India, 2012\\
\noindent \textcolor{highlightcolor}{\textbf{\textit{Grade}}}: 8.3/10 (equivalent to a German grade of 1.3)

\noindent{\rule{\linewidth}{1.4pt}}
\textbf{AWARDS \& HONOURS}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

\vspace{0.1cm}
\noindent \textbf{Best Presentation Award 2015}\\
An adaptive approach to real-time estimation of vehicle dynamics parameters using kalman filtering.\\

\noindent \textbf{Best Presentation Award 2014}\\
Optimization of vehicle parameters based on lap-time simulations using multi-objective evoluation algorithm.

\noindent{\rule{\linewidth}{1.4pt}}
\textbf{CERTIFICATION \& PROFESSIONAL DEVELOPMENT}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

\noindent Demonstrated cross-cultural team leadership $\vert$ Implemented ISO-26262 functional safety requirements.

\noindent{\rule{\linewidth}{1.4pt}}
\textbf{LANGUAGES}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

\noindent English (Proficient) {$\vert$} German (Proficient) $\vert$ Tamil (Native) $\vert$ Hindi (Advanced)

\noindent{\rule{\linewidth}{1.4pt}}
\textbf{ADDITIONAL PROJECTS}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

\vspace{0.3cm}
\noindent
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{Custom PCB for Bluetooth Remote – DIY Electric Skateboard} & \textbf{2023}
\end{tabular}

{\small
\begin{itemize}
    \item[$\textcolor{highlightcolor}{\checkmark}$]  
    Designed and built a custom PCB for a Bluetooth remote to control a self-built electric skateboard.
\end{itemize}
}

\vspace{0.3cm}
\noindent
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{Raspberry Pi Powered Smart-Home Network} & \textbf{2020}
\end{tabular}

{\small
\begin{itemize}
    \item[$\textcolor{highlightcolor}{\checkmark}$]  
            Built a versatile Raspberry-Pi smart home network with
            remote-access, custom file storage server with automatic backups
            using rsync, Zigbee2Mqtt server for controlling IOT devices using
            siri/google-nest and custom automations.
\end{itemize}
}

\vspace{0.3cm}
\noindent
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{Machine Learing Suite} & \textbf{2015}
\end{tabular}

{\small
\begin{itemize}
    \item[$\textcolor{highlightcolor}{\checkmark}$]  
        Implement a deep convolution neural network for optical character recognition as part of a freelance software project in MATLAB. Used MEX API to increase performance. 
\end{itemize}
}

\vspace{0.3cm}
\noindent
\begin{tabular}{ @{\hskip 0pt}m{0.77\textwidth} >{\raggedleft\arraybackslash}p{0.2\textwidth} }
    \noindent\textbf{Driver-in-the-Loop Simulator} & \textbf{2014}
\end{tabular}

{\small
\begin{itemize}
    \item[$\textcolor{highlightcolor}{\checkmark}$]  
    Implemented a driver-in-the-loop simulator by coupling IPG CarMaker and MATLAB/Simulink.
\end{itemize}
}

\noindent{\rule{\linewidth}{1.4pt}}
\textbf{SELECTED PUBLICATIONS*}

\vspace{-0.1cm}
\noindent{\rule{\linewidth}{0.01cm}}

{\small 
    \noindent \textbf{Gnanasambandham}, C.; Fleissner, F.; Eberhard, P.: Enhancing the dissipative properties of PDs using rigid obstacle-grids. Journal of Sound and Vibration, 2020.\\
    \noindent \textbf{Gnanasambandham}, C.; Stender, M.; Hoffmann, N.; Eberhard, P.: Multi-scale dynamics of PDs using wavelets: Extracting particle activity metrics from ring down experiments. Journal of Sound Vibration, 2019.\\ \\
    \noindent \textbf{*}for a complete list of publications, visit my \href{https://scholar.google.com/citations?user=azp3ffYAAAAJ&hl=de}{\textcolor{highlightcolor}{\underline{Google Scholar Profile}}} 
}



\end{document}

